Millions of Type Errors

### 2023-04-05 oopsla23/paper.tex
count mismatch explanation
more overview figures
2 tables
horizontal bars could work too,

    \code{IncorrectGenericParameterCount} & Arity mismatch for a generic type \\
    \code{CountMismatch} & \FILL{} \\
    \code{UnknownProperty} & Referenced an invalid field or method  \\
    \code{OnlyTablesCanHaveMethods} & Tried to attach a method to a non-table \\
    \code{CannotCallNonFunction} & Called a value that is not a function \\
    \code{TypesAreUnrelated} & Failed to cast, unify, or check subtyping \\
    \code{TypeMismatch} & Generic label for other type errors \\
    \code{GenericError}
    & Generic label for other errors, e.g., declaring a \\
    & \quad{} supertype that is not a class type
    %% or iterated over a table without specifying how

@@

  1,146 & sessions \\
  & \begin{tabular}{l}
      1,143 single mode = 1046 nocheck + 94 nonstrict + 3 strict \\
      detected 2 multi-mode projects, 2 mode upgrades, 2 mode downgrades
    \end{tabular}
\end{tabular}
  \caption{Dataset overview}
  \label{f:dataset-overview}
\end{figure}

>>>>

    \code{CountMismatch} & Arity mismatch for a function \\
    \code{IncorrectGenericParameterCount} & Arity mismatch for a generic type \\
    \code{UnknownProperty} & Referenced an invalid field or method  \\
    \code{OnlyTablesCanHaveMethods} & Tried to attach a method to a non-table \\
    \code{CannotCallNonFunction} & Called a value that is not a function \\
    \code{TypesAreUnrelated} & Failed to cast, unify, or check subtyping \\
    \code{TypeMismatch} & Generic label for other type errors \\
    \code{GenericError}
    & Generic label for other non-type errors, such as looping\!\!\! \\
    & over a table without a clear iteration strategy
    %% & {}~~declaring a supertype that is not a class type

@@

  1,146 & sessions \\
  & \begin{tabular}{l}
      1,143 single mode = 1046 nocheck + 94 nonstrict + 3 strict \\
      detected 2 multi-mode projects, 2 mode upgrades, 2 mode downgrades
    \end{tabular}
\end{tabular}

  \begin{minipage}{0.5\textwidth}
    \begin{tabular}{rr}
      Session length & \# Sessions \\\midrule
      1 &  450 \\
      2 &  199 \\
      3 &  129 \\
      4 &  73 \\
      5 &  60 \\
      6-10 & 150 \\
      11-20 & 67 \\
      21-40 & 11 \\
      >40 & 7
      %% max 393
    \end{tabular}
  \end{minipage}\begin{minipage}{0.5\textwidth}
    \begin{tabular}{rr}
      Time delta & \# Records \\\midrule
      <=0ms & 0 \\
      0-5ms & 284 \\
      5-1000ms & 248 \\
      1-2s & 153 \\
      2-5s & 232 \\
      5-10s & 207 \\
      10-30s & 524 \\
      30-60s & 392 \\
      1-2m & 394 \\
      2-5m & 559 \\
      5-10m & 360 \\
      >10-60m & 502
    \end{tabular}
  \end{minipage}

  \caption{Dataset overview}
  \label{f:dataset-overview}
\end{figure}
